The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-17 paper/mri_paper.tex
fixed fig refs

From the behavior of the second order velocity perturbations (Figure \ref{u_secondorder_by_Pm}) in the bulk of the flow (i.e. apart from the boundary layers), we gather that the MRI is saturating via a background shear reduction. Recall that the linear shear profile means that the background shear is positive for negative values of $x$ and negative for positive values of $x$. Thus Figure \ref{u_secondorder_by_Pm} shows the azimuthal velocity perturbations resisting the background shear in the bulk of the flow

>>>>

From the behavior of the second order velocity perturbations (Figure \ref{stress_uy_cuts}) in the bulk of the flow (i.e. apart from the boundary layers), we gather that the MRI is saturating via a background shear reduction. Recall that the linear shear profile means that the background shear is positive for negative values of $x$ and negative for positive values of $x$. Thus Figure \ref{stress_uy_cuts} shows the azimuthal velocity perturbations resisting the background shear in the bulk of the flow.
